%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     J. CATRIEL LOPEZ - CV
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{J. Catriel}{Lopez}{ 
\href{mailto:jcatriel.lopez@gmail.com}{jcatriel.lopez@gmail.com} | +54 0249 15 4528397 | Tandil, Buenos Aires, Argentina
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github: \href{https://github.com/JCatrielLopez}{\custombold{JCatrielLopez}} \\
LinkedIn: \href{https://www.linkedin.com/in/JCatrielLopez/}{\custombold{JCatrielLopez}} \\
Dev.to: \href{https://dev.to/catriel}{\custombold{Catriel}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Systems Engineer}
\descript{U. N. I. C. E. N}
\location{Expected 2021}

%
%\sectionsep
%\subsection{High School}
%\descript{Sagrada Familia}
%\location{2013}
%
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming and Tools}
\location{Programming Languages:}
Python \textbullet{}   Java \textbullet{}  R \\
\location{Tools}
Pandas \textbullet{} NumPy \textbullet{} Excel \textbullet{} 
Shiny \textbullet{} PostgreSQL \textbullet{} Tensorflow \textbullet{} Keras \textbullet{} Scrapy \textbullet{} bs4 \\
\location{Others}
Bash \textbullet{} Linux
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LANGUAGES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Languages}
\location{Native:} Spanish \\
\location{Proficient:} English
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Teaching Assistant}
\descript{| "Tecnologia de la informacion en organizaciones" - T. U. D. A. I}
\location{ Aug 2020 – Dic 2020}
\vspace{\topsep} % Fix for awkward extra vertical space
\begin{tightemize}
\item Worked with students in class, to help answer any question they had.
\item Graded projects and exams.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\runsubsection{Title}
\descript{| Graduate Thesis }
\begin{tightemize}
\item Currently working on visiting patterns and
automatic labeling of places from smartphone data.
\item Based on data collected on Ayacucho, Bs. As.
\item Currently being developed on R.
\end{tightemize}
\sectionsep

\runsubsection{
\href{https://github.com/JCatrielLopez/InvOp-Comedor-UNICEN}{Queue-Based Monte Carlo Analysis to Improve Lunch Times on Campus}}
\descript{| College Coursework}
\begin{tightemize}
\item Final work for the "Operations Research" course.
\item We developed a Monte Carlo simulation of an everyday scenario for the dining hall on campus and proposed two solutions for the long queue times.
\item We analyzed how our solutions impacted the queue times and presented the conclusions on a Shiny dashboard.
\item Implemented on R and Python.
\end{tightemize}
\sectionsep

\runsubsection{\href{https://github.com/JCatrielLopez/magritte-cloud}{RAYMAN}}
\descript{| College Coursework}
\begin{tightemize}
\item Final work for the "Software engineering" course
\item A Feature Driven Design of a Personal Health Record app for Android.
\item I was involved in the design and implementation of the cloud server and database needed.
\item Developed in Java and PostgreSQL, using Spring.
\end{tightemize}
\sectionsep


\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSES AND CERTIFICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Courses and Certifications} 

\begin{tabular}{rll}
2019   & \custombold{Fundamentals of Deep Learning for Computer Vision}\\
       & (NVIDIA Deep Learning Institute)\\
2018   & \custombold{Machine Learning para Seguridad en Redes y Detección}\\
       & \custombold{de Malware}\\
       & (Congreso Argentino de Ciencias de la Computación)\\
2017   & \custombold{Experto Universitario en Seguridad de la Información}\\
       & (Universidad Técnica Nacional) — \\
2017   & \custombold{Modelado de Sistemas Orientados a Objetos con Rational}\\
       & (U. N. I. C. E. N)\\
2015   & \custombold{Internet of Things}\\
       & (Centro de Innovación y Creación de Empresas)\\
2015   &  \custombold{Historia del Software Libre}\\
       & (Festival Latinoamericano de Instalación de Software Libre)\\
2015   &  \custombold{Taller de Introducción a Arduino}\\  
       &  (U. N. I. C. E. N)\\
\end{tabular}
\sectionsep

\end{minipage} 
\end{document}

\documentclass[]{article}

\subsection{Systems Engineer}

